\textbf{Computational Fuzzy Extractors}

### 2013-04-11 trunk/CompFuzzExt.tex
minor edits to 3, 3.1, and clarifiying the proof in appendix C.2

@@

\newcommand{\metric}{\ensuremath{\mathtt{Metric}}\xspace}
\newcommand{\hill}{\ensuremath{\mathtt{HILL}}\xspace}
\newcommand{\hillrlx}{\ensuremath{\mathtt{HILL-rlx}}\xspace}
\newcommand{\yao}{\ensuremath{\mathtt{Yao}}\xspace}
\newcommand{\unp}{\ensuremath{\mathtt{unp}}\xspace}
\newcommand{\metricstar}{\ensuremath{\mathtt{Metric}^*}\xspace}
\newcommand{\metricd}{\ensuremath{\mathtt{Metric}^*\mathtt{-d}}\xspace}
\newcommand{\hillstar}{\ensuremath{\mathtt{HILL}^*}\xspace}
\newcommand{\hillprime}{\ensuremath{\mathtt{HILL'}}\xspace}
\newcommand{\metricprime}{\ensuremath{\mathtt{Metric'}}\xspace}
\newcommand{\metricprimestar}{\ensuremath{\mathtt{Metric'}^*}\xspace}
\newcommand{\hillprimestar}{\ensuremath{\mathtt{HILL'}^*}\xspace}
\newcommand{\poly}{\ensuremath{\mathtt{poly}}\xspace}
\newcommand{\rank}{\ensuremath{\mathtt{rank}}\xspace}
\newcommand{\ngl}{\ensuremath{\mathtt{ngl}}\xspace}
\newcommand{\Hoo}{\mathrm{H}_\infty}
\newcommand{\Hav}{\tilde{\mathrm{H}}_\infty}
\newcommand{\Dom}{\mathsl{Dom}}
\newcommand{\Range}{\mathsl{Rng}}
\newcommand{\Keys}{\mathsl{Keys}}
\def\col{\mathrm{Col}}

@@

%=============================================================
\section{Impossibility of Computational Secure Sketches}
\label{sec:defCompFuzzyExtractors}
In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational entropy than information theoretic entropy.  %We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch is at most $n - |B_t(\cdot)|$.  For comparison, random linear codes achieve unpredictability $n(1-o(1)) - B_t(\cdot) $.

@@

\subsection{Bounds on Secure Sketches using HILL entropy}
\label{sec:imp HILL sketch}
HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.  It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}, here we recall a weaker definition due to Gentry and Wichs~\cite{gentry2011separating}~(the term relaxed HILL entropy was introduced in~\cite{reyzin2011some}).

\begin{definition}
Let $(W, X)$ be a pair of random variables.  $W$ has 
\emph{relaxed HILL entropy} at least $k$ conditioned on $X$,
denoted $H^{\hill-rlx}_{\epsilon, s_{sec}}(W|X)\geq k$ if there exists a joint distribution $(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, X),(Y,Z))\leq \epsilon$.
\end{definition}

@@

We can now formalize the intuition above.  A sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{sam}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Let $s_{rec}$ denote the size of the circuit that computes $\rec$.  If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $C$ with $|C|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

@@

\subsection{Proof of \thref{thm:impSketchArbitraryW}}
\label{sec:proof of thm sketch implies code}
\begin{proof}
  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(Y, Z)$ be a joint distribution such that $\Hav(Y | Z)\geq k$ and
\[ 
\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, Z))<\epsilon.
\]  
where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(Y, Z)$ must exist by the definition of conditional HILL entropy.
%Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$. Let $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $s=O(s_{neigh}+s_{rec})$.  This implies that $H^{\hill}_{\epsilon, s}(X|\sketch(X))\geq k$.  
Define $D$ as:
\begin{enumerate}
\item Input $y\in\mathcal{M}, z \in\{0, 1\}^*, t$.
\item For all $1\leq t'\leq t$: 
\subitem  $y'\leftarrow \sample(y, t')$.
\subitem If $\rec(y', z) \neq  y$ output $0$.
\item Output $1$.
\end{enumerate}
 By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
$\delta^D((W, \sketch(W)), (Y, Z))<\epsilon$, we know $\Pr[D(Y, Z) = 1]>1-\epsilon-t\delta$.  By Markov's inequality,  there exists a set $S_Z$ such that $\Pr[Z\in S_Z]\ge 1/2$ and for all $z\in S_Z$, $\Pr[ D(Y|z, z) =1]> 1- 2(\epsilon + t\delta)$.  Moreover, by \cite[Lemma 2.2a]{DBLP:journals/siamcomp/DodisORS08} (which is derived simply via Markov's inequality applied to the positive random variable $\max_y \Pr[Y_s=y]$), there exists a set $S'_Z$ such that $\Pr[z\in S'_Z]> 1/2$ and for all $z\in S'_Z$, $\Hoo(Y | z)\ge k-1$. \lnote{simplified this derivation}\bnote{I don't believe this fix}  Fix one value $z \in S_Z\cap S'_Z$ (which exists because the sum of probabilities of $S_Z$ and $S'_Z$ is greater than 1).  
Thus, for all such that $t', 1\leq t'\leq t$, 
\[ \Pr_{y\leftarrow Y|z}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]> 1-2(\epsilon+t\delta).\]  
%Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
Thus,  $Y|z$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,s)$ and $2^{k-1}$ points.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
\end{proof}

>>>>

\mathchardef\mhyphen="2D

@@

\newcommand{\metric}{\ensuremath{\mathtt{Metric}}\xspace}
\newcommand{\hill}{\ensuremath{\mathtt{HILL}}\xspace}
\newcommand{\hillrlx}{\ensuremath{\mathtt{HILL\mhyphen rlx}}\xspace}
\newcommand{\yao}{\ensuremath{\mathtt{Yao}}\xspace}
\newcommand{\unp}{\ensuremath{\mathtt{unp}}\xspace}
\newcommand{\metricstar}{\ensuremath{\mathtt{Metric}^*}\xspace}
\newcommand{\metricd}{\ensuremath{\mathtt{Metric}^*\mathtt{-d}}\xspace}
\newcommand{\hillstar}{\ensuremath{\mathtt{HILL}^*}\xspace}
\newcommand{\hillprime}{\ensuremath{\mathtt{HILL'}}\xspace}
\newcommand{\metricprime}{\ensuremath{\mathtt{Metric'}}\xspace}
\newcommand{\metricprimestar}{\ensuremath{\mathtt{Metric'}^*}\xspace}
\newcommand{\hillprimestar}{\ensuremath{\mathtt{HILL'}^*}\xspace}
\newcommand{\poly}{\ensuremath{\mathtt{poly}}\xspace}
\newcommand{\rank}{\ensuremath{\mathtt{rank}}\xspace}
\newcommand{\ngl}{\ensuremath{\mathtt{ngl}}\xspace}
\newcommand{\Hoo}{\mathrm{H}_\infty}
\newcommand{\Hav}{\tilde{\mathrm{H}}_\infty}
\newcommand{\Dom}{\mathsl{Dom}}
\newcommand{\Range}{\mathsl{Rng}}
\newcommand{\Keys}{\mathsl{Keys}}
\def\col{\mathrm{Col}}

@@

%=============================================================
\section{Impossibility of Computational Secure Sketches}
\label{sec:defCompFuzzyExtractors}
In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational than information-theoretic entropy.  We consider two different notions for computational entropy, and for both of them show that we can do essentially as well information-theoretically as computationally.

%We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $n - |B_t(\cdot)|$.  Since random linear codes already achieve min-entropy $n(1-o(1)) - B_t(\cdot)$ on uniform inputs, it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs. \lnote{$B_t$ notation is not correct here -- it denotes the ball, not the logarithm of its volume} \lnote{Should we say something about efficiency of decoding?  Also, should we be clearer that these bounds are tight for uniform inputs and Hamming metric, but not necessarily otherwise? Perhaps just a pointer to the last part of this section (which could be called 3.3?}

@@

\subsection{Bounds on Secure Sketches using HILL entropy}
\label{sec:imp HILL sketch}
HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.  It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}. Here we recall a weaker definition due to Gentry and Wichs~\cite{gentry2011separating}~(the term relaxed HILL entropy was introduced in~\cite{reyzin2011some}); since we show impossibility even for this weaker definition, impossibility for the stronger definition follows immediately.

\begin{definition}
Let $(W, X)$ be a pair of random variables.  $W$ has 
\emph{relaxed HILL entropy} at least $k$ conditioned on $X$,
denoted $H^{\hillrlx}_{\epsilon, s_{sec}}(W|X)\geq k$ if there exists a joint distribution $(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, X),(Y,Z))\leq \epsilon$.
\end{definition}

@@

We can now formalize the intuition above and show that a sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{sam}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Let $s_{rec}$ denote the size of the circuit that computes $\rec$.  If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $C$ with $|C|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

@@

\subsection{Proof of \thref{thm:impSketchArbitraryW}}
\label{sec:proof of thm sketch implies code}
\begin{proof}
  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(Y, Z)$ be a joint distribution such that $\Hav(Y | Z)\geq k$ and
\[ 
\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, Z))<\epsilon.
\]  
where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(Y, Z)$ must exist by the definition of conditional HILL entropy. Let $Y_z$ denote the random variable $Y|Z=z$.
%Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$. Let $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $s=O(s_{neigh}+s_{rec})$.  This implies that $H^{\hill}_{\epsilon, s}(X|\sketch(X))\geq k$.  
Define $D$ as:
\begin{enumerate}
\item Input $y\in\mathcal{M}, z \in\{0, 1\}^*, t$.
\item For all $1\leq t'\leq t$: 
\subitem  $y'\leftarrow \sample(y, t')$.
\subitem If $\rec(y', z) \neq  y$ output $0$.
\item Output $1$.
\end{enumerate}
 By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
$\delta^D((W, \sketch(W)), (Y, Z))<\epsilon$, we know $\Pr[D(Y, Z) = 1]>1-\epsilon-t\delta$.  By Markov's inequality,  there exists a set $S_Z$ such that $\Pr[Z\in S_Z]\ge 1/2$ and for all $z\in S_Z$, $\Pr[ D(Y_z, z) =1]> 1- 2(\epsilon + t\delta)$.

Because $\Hav(Y | Z)\geq k$, we know that $\expe_{z\leftarrow Z} \max_y \Pr[Y_z=y]\geq 2^k$.  Applying Markov's inequality to the random variable $\max_y \Pr[Y_z=y]$, there exists a set $S'_Z$ such that $\Pr[z\in S'_Z]> 1/2$, and for all $z\in S'_Z$, $\Hoo(Y_z)\ge k-1$ (we can use the strict version of Markov's inequality here, because the random variable $\max_y \Pr[Y_z=y]$ is positive).  Fix one value $z \in S_Z\cap S'_Z$ (which exists because the sum of probabilities of $S_Z$ and $S'_Z$ is greater than 1).  
Thus, for all such that $t', 1\leq t'\leq t$, 
\[ \Pr_{y\leftarrow Y_z}[y'\leftarrow \sample(y, t') \wedge \rec(y',z) = y]> 1-2(\epsilon+t\delta).\]  
%Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
Thus,  $Y_z$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,z)$ and $2^{k-1}$ points.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
\end{proof}
